---
title: "FIFA 19"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: menu
    source_code: https://github.com/laceto/fifa19-data-visualization
    theme: simplex

---

<!-- Learn more about flexdashboard at https://rstudio.github.io/flexdashboard -->


```{r setup, include=FALSE}
library(dplyr)
library(readxl)
library(shiny)
library(ggplot2) # devtools::install_github('hadley/ggplot2')
library(readxl)
library(dplyr)
library(flexdashboard) # devtools::install_github('rstudio/flexdashboard')
library(shinyWidgets)
library(stringr)
library(tibble)
library(scales)
library(ggradar)
library(ggiraphExtra)
options(scipen=999)

full_tracts <- readxl::read_xlsx("./fifa19.xlsx", sheet = "selection") %>%
  # dplyr::sample_n(100) %>%
  dplyr::filter(!is.na(Position))

position <- tibble(Position = c("CF", "ST", "RS", "LS", "RF", "LW","LM","CDM", "LDM", "RDM", "CM", "LCM", "RCM", "CAM", "LAM", "RM","RW", "LWB", "LB", "LCB", "CB", "RB", "RCB", "RWB", "GK"),
                   Role = c(rep("Striker", 5), rep("Midfielder", 12), rep("Defender", 7), "Goalkeeper"))

full_tracts <- full_tracts %>%
  dplyr::left_join(., position, by = "Position") %>%
  dplyr::filter(!is.na(Role)) %>%
  dplyr::mutate(Value = if_else(stringr::str_extract(stringr::str_replace(Value, "\\\200", ""), "[:alpha:]") == "M", 1000000, 1000) * as.numeric(stringr::str_extract(stringr::str_replace(Value, "\\\200", ""), "\\d+")),
                Weight = stringr::str_replace(Weight, "lbs", ""),
                Height = stringr::str_replace_all(Height, "'", "."),
                Weight = as.numeric(Weight),
                Height = as.numeric(Height),
                Wage = if_else(stringr::str_extract(stringr::str_replace(Wage, "\\\200", ""), "[:alpha:]") == "M", 1000000, 1000) * as.numeric(stringr::str_extract(stringr::str_replace(Wage, "\\\200", ""), "\\d+")),
                Wage = Wage * 12) %>%
  dplyr::filter(!is.na(Value))

selectedData <- reactive({
  if(input$Nationality == "All") {
    full_tracts %>%
    dplyr::select(Name, Age, Overall, Club, Value, Wage, Role, Position, Height, Weight)
  } else {
  data <- full_tracts %>%
    dplyr::filter(Nationality == input$Nationality,
                  Value >= input$Value * 1000000) %>%
    dplyr::select(Name, Age, Overall, Club, Value, Wage, Role, Position, Height, Weight)
  }
})

selectedDataClub <- reactive({
  full_tracts %>%
    dplyr::filter(Club == input$Club) %>%
    dplyr::select(Name, Age, Overall, Club, Value, Wage, Role, Position, Height, Weight, `Preferred Foot`)
})

```

<!-- Sidebar {.sidebar} -->
<!-- ====================================================================== -->

```{r}

# Define inputs
# selectInput('Nationality', label = 'Select a Nationality', choices = unique(full_tracts$Nationality), selected = "Italy")

# pickerInput(
#       inputId = "Nationality", 
#       label = "Select a Nationality", 
#       choices = sort(c("All", unique(full_tracts$Nationality))), 
#       selected = "All",
#       options = list(
#         `actions-box` = TRUE
#       ), 
#       multiple = TRUE
#     )

```

<!-- Use the __explore nationality__ tab to explore neighborhood diversity for your chosen metropolitan area in 2010.  The red line on the scatterplot represents a locally-weighted estimate of how diversity varies in the metropolitan area by distance from its urban core or cores.  Click and drag on the scatterplot to highlight the corresponding Census tracts on the map below, and click on a Census tract on the map to generate a chart of race and ethnicity counts.   -->

<!-- Click the __Compare over time__ tab to examine how locally-weighted estimates of neighborhood diversity by distance from the urban core has varied between the 1990, 2000, and 2010 Censuses, and view maps of these shifts over time. To learn more about the project, click the __About__ tab.   -->

<!-- Application author: [Kyle Walker](http://personal.tcu.edu/kylewalker), [Texas Christian University](http://www.tcu.edu) -->

Explore Nationality
======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}

pickerInput(
      inputId = "Nationality",
      label = "Select a Nationality",
      choices = sort(c("All", unique(full_tracts$Nationality))),
      selected = "All",
      options = list(
        `actions-box` = TRUE
      ),
      multiple = TRUE
    )

shiny::numericInput(inputId = "Value", "Player value greather then (in M)", min = 1, max = max(full_tracts$Value), value = 20)

```


Row
-----------------------------------------------------------------------

### Table all players from selected Nationality

```{r}

renderTable({
  selectedData()
})
```

Row 
-----------------------------------------------------------------------

### Playing Roles

```{r}

renderPlot(
  ggplot(selectedData(), aes(Role)) + 
  geom_bar(aes(col = "orange", fill = ..count..)) + 
  scale_fill_distiller(palette = "Reds", direction = 1) +
  ggtitle("Distribution of Players based on General Playing Roles") + 
  theme_minimal() + 
  theme(legend.position = 'none')
)
```

### Playing Positions

```{r}


renderPlot(
  ggplot(selectedData(), aes(Position)) + 
  geom_bar(aes(col = "orange", fill = ..count..)) + 
  scale_fill_distiller(palette = "Reds", direction = 1) +
  ggtitle("Distribution of Players based on Best Positions") + 
  theme_minimal() + 
  theme(legend.position = 'none')
)


```

Row 
-----------------------------------------------------------------------

### Age Distribution

```{r}

renderPlot(
  selectedData() %>%
  ggplot2::ggplot(data = ., aes(Age)) + 
  geom_histogram(binwidth = 1, col = "orange", aes(fill = ..count..)) + 
  scale_fill_distiller(palette = "Reds", direction = 1) +
  ggtitle("Distribution based on Age") + 
  theme_minimal() +
  theme(legend.position = 'none')
)


```

### Age Distribution and Roles

```{r}

renderPlot(
  selectedData() %>%
  ggplot2::ggplot(data = ., aes(Age)) + 
  geom_density(col = "orange", aes(fill = Role), alpha = 0.5) +
  facet_grid(.~Role) + 
  ggtitle("Distribution based on Age and Role") + 
  theme_light() +
  theme(legend.position = 'none')
)


```

Row 
-----------------------------------------------------------------------

### Distribution by Overall Rating

```{r}

# g_overall <- ggplot(data = selectedData(), aes(Overall))


renderPlot(
  ggplot(data = selectedData(), aes(Overall)) + 
  geom_histogram(binwidth = 2, col = "orange", aes(fill = ..count..)) + 
  scale_fill_distiller(palette = "Reds", direction = 1) +
  ggtitle("Distribution based on Overall Rating") + 
  theme_minimal() +
  theme(legend.position = 'none')
)


```

### Distribution by Player Value

```{r}




renderPlot(
  ggplot(selectedData() %>% dplyr::filter(Value >= input$Value * 1000000), aes(x = Value)) +
  geom_bar(aes(col = "orange", fill = ..count..)) +
  scale_fill_distiller(palette = "Reds", direction = 1) +
  ggtitle("Distribution of Value between 50M–100M+") +
  theme_minimal() +
  theme(legend.position = 'none')
)


```




Explore Club
============================================================================

Inputs {.sidebar}
-------------------------------------

```{r}

# Define inputs
pickerInput(
      inputId = "Club",
      label = "Select a Club",
      choices = sort(unique(full_tracts$Club)),
      selected = "Inter",
      options = list(
        `actions-box` = TRUE
      ),
      multiple = FALSE
    )

shiny::sliderInput(inputId = "top_n", "How many top players", min = 1, max = 10, value = 5)

```

<!-- Row -->
<!-- ---------------------------------------------------------------------------- -->

<!-- ### Table all players from selected Club -->

<!-- ```{r} -->

<!-- renderTable({ -->
<!--   selectedDataClub() -->
<!-- }) -->

<!-- ``` -->
Row
-----------------------------------------------------------------------------

### 

```{r}

renderValueBox({
      valueBox(
        paste0(round(sum(selectedDataClub()$Value) / 1000000, 2), " Total value"), icon = icon("list"),
        color = "info"
      )
    })

```

### 

```{r}

renderValueBox({
      valueBox(
        paste0(round(mean(selectedDataClub()$Value) / 1000000, 2), " Mean value"), icon = icon("list"),
        color = "info"
      )
    })

```

### 

```{r}

renderValueBox({
      valueBox(
        paste0(round(sum(selectedDataClub()$Wage) / 1000000, 2), " Total Wage"), icon = icon("list"),
        color = "info"
      )
    })

```

Row
-----------------------------------------------------------------------------

### Top Players by Value

```{r}

renderPlot(
  
  selectedDataClub() %>%
  dplyr::arrange(desc(Value)) %>%
  head(input$top_n) %>% 
  ggplot(., aes(x = reorder(Name, Value), y = Value)) + 
  labs(x = 'Name') +
  geom_bar(stat = "identity", aes(col = "orange", fill = Value)) + 
  coord_flip() + 
  # scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6)) +
  scale_fill_distiller(palette = "Reds", direction = 1) +
  ggtitle("Top Players") + 
  theme_minimal() +
  theme(legend.position = 'none')
)

```

### Preferred Foot

```{r}


renderPlot(
  
  selectedDataClub() %>%
  dplyr::count(`Preferred Foot`) %>%
  dplyr::mutate(n = as.numeric(n)) %>%
  ggplot(., aes(x="", y=n, fill=`Preferred Foot`)) +
  geom_bar(width = 1, stat = "identity") + coord_polar("y", start=0) +
  scale_fill_brewer(palette = "Reds", direction = 1) +
  theme_minimal()+
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.border = element_blank(),
    panel.grid=element_blank(),
    axis.ticks = element_blank(),
    plot.title=element_text(size=14, face="bold")
  ) +
  theme(axis.text.x=element_blank()) +
  ggtitle("Most preferred foot")
)

```

Row
-----------------------------------------------------------------------------

### Top Players by Weight

```{r}

renderPlot(
  
  selectedDataClub() %>%
  dplyr::arrange(desc(Weight)) %>%
  head(input$top_n) %>% 
  ggplot(., aes(x = reorder(Name, Weight), y = Weight)) + 
  labs(x = 'Name') +
  geom_bar(stat = "identity", aes(col = "orange", fill = Weight)) + 
  coord_flip() + 
  # scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6)) +
  scale_fill_distiller(palette = "Reds", direction = 1) +
  ggtitle("Top Players") + 
  theme_minimal() +
  theme(legend.position = 'none')
)

```

### Top Players by Height

```{r}

renderPlot(
  
  selectedDataClub() %>%
  dplyr::arrange(desc(Height)) %>%
  head(input$top_n) %>% 
  ggplot(., aes(x = reorder(Name, Height), y = Height)) + 
  labs(x = 'Name') +
  geom_bar(stat = "identity", aes(col = "orange", fill = Height)) + 
  coord_flip() + 
  # scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6)) +
  scale_fill_distiller(palette = "Reds", direction = 1) +
  ggtitle("Top Players") + 
  theme_minimal() +
  theme(legend.position = 'none')
)

```



Compare Clubs
============================================================================

Inputs {.sidebar}
-------------------------------------

```{r}

# Define inputs
pickerInput(
      inputId = "Club1",
      label = "Select a Club to compare",
      choices = sort(unique(full_tracts$Club)),
      selected = "Inter",
      options = list(
        `actions-box` = TRUE
      ),
      multiple = FALSE
    )

pickerInput(
      inputId = "Club2",
      label = "Select a Club to compare",
      choices = sort(unique(full_tracts$Club)),
      selected = "Juventus",
      options = list(
        `actions-box` = TRUE
      ),
      multiple = FALSE
    )

pickerInput(
      inputId = "role",
      label = "Select a role to compare",
      choices = sort(unique(full_tracts$Role)),
      selected = "Goalkeeper",
      options = list(
        `actions-box` = TRUE
      ),
      multiple = FALSE
    )

```

Row
-----------------------------------------------------------------------

### Radar Comparison

```{r}

tocompare <- reactive({
  data <- full_tracts %>%
    dplyr::filter(Club %in% c(input$Club1, input$Club2)) %>%
    dplyr::select(Club, Role, Crossing:GKReflexes) %>%
  mutate(across(where(is.numeric), rescale, na.rm = TRUE)) %>%
  tidyr::pivot_longer(cols = c("Crossing":"GKReflexes"), names_to = "Feature", values_to = "value") %>%
  dplyr::group_by(Club, Feature) %>%
  dplyr::summarise(value = mean(value)) %>%
  tidyr::pivot_wider(names_from = "Feature", values_from = "value")
  return(data)
})

renderPlot(ggradar(tocompare()))

```

### Radar Comparison by Role

```{r}

tocompare2 <- reactive({
  data <- full_tracts %>%
    dplyr::filter(Club %in% c(input$Club1, input$Club2), Role == input$role) %>%
    dplyr::select(Club, Role, Crossing:GKReflexes) %>%
  mutate(across(where(is.numeric), rescale, na.rm = TRUE)) %>%
  tidyr::pivot_longer(cols = c("Crossing":"GKReflexes"), names_to = "Feature", values_to = "value") %>%
  dplyr::group_by(Club, Feature) %>%
  dplyr::summarise(value = mean(value)) %>%
  tidyr::pivot_wider(names_from = "Feature", values_from = "value")
  return(data)
})

renderPlot(ggradar(tocompare2()))

```


Row
-----------------------------------------------------------------------

### Pyramid Age

```{r}

data <- reactive({
  data <- full_tracts %>%
    dplyr::filter(Club %in% c(input$Club1, input$Club2)) %>%
    dplyr::count(Club, Age)
  
  data <- data %>%
    dplyr::count(Club) %>%
    dplyr::mutate(direction = c(-1, 1),
                  n = NULL,
                  sign2 = NULL) %>%
    dplyr::right_join(
      full_tracts %>%
        dplyr::filter(Club %in% c(input$Club1, input$Club2)) %>%
        dplyr::count(Club, Age)
      ) %>%
    dplyr::mutate(max_n = max(n),
                  n = n * direction,
                  direction = NULL)
  
  return(data)
})

max_n <- reactive({
  max_n <- data()$max_n[1]
  return(max_n)
})

renderPlot(
  data() %>%
  ggplot(aes(x = Age, fill = Club,
                 y = n)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = abs, limits = max_n() * c(-1,1)) +
  coord_flip() +
  scale_fill_brewer(palette = "Reds")
)

```

### Overall by Preferred Foot 

```{r}

data2 <- reactive({
  data2 <- full_tracts %>%
    dplyr::filter(Club %in% c(input$Club1, input$Club2))
  return(data2)
})



renderPlot(
   
  ggplot2::ggplot(data2(), aes(x = Role, y = Overall)) + 
  geom_bar(
    aes(fill = Club), stat = "identity", color = "white",
    position = position_dodge(0.9)
    ) + 
  # labs(title = "TipoEvento by Antidurata") +
  scale_fill_brewer(palette = "Reds") + 
  facet_wrap(~`Preferred Foot`)
)

```

About
============================================================================

Questa dashboard descrive e analizza il dataset dei giocatori del famoso gioco FIFA 19.  
Per velocizzare il caricamento dei dati sono state selezionate solo squadre relative al campionato Italiano e spagnolo.  
L'applicazione permette all'utente di visualizzare alcune fondamentali caratteristiche di un calciatore, nonchè statistiche riguardanti la nazionalità dei giocatori stessi e il confronto tra due club diversi. 

I dati e il codice utilizzati possono essere scaricati dalla mia repo [github](https://github.com/laceto/fifa19-data-visualization).  
L'applicazione è stata costruita con un file .Rmd e decorato con alcune funzioni dei pacchetti [Shiny](http://shiny.rstudio.com) e [flexdashboard](http://rstudio.github.io/flexdashboard/index.html).  



<style>

#sidebar.section.sidebar {

  background-color: white; 
  font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif !important;

}

.js-irs-0 .irs-bar {
border-top-color: #d01010;
border-bottom-color: #d01010;
} 

.js-irs-0 .irs-bar-edge {
border-color: #d01010;
}

.js-irs-0 .irs-single, .js-irs-0 .irs-bar-edge, .js-irs-0 .irs-bar {
background: #a00;
}

</style>




